\TheCommand{exec}%
\Command{exec [handler: handler] [destroyer: destroyer] [watchdog: \\
watchdog] [timeout: duration] [successExitValue: number]\\~
[successExitValues: list] [terminal: false|true]\\~
[terminalCommand: command] command [env] [path]}

\TypeTable{exec \\}{%
% properties
handler \\
destroyer \\
watchdog \\
timeout \\
terminal \\
terminalCommand \\
env \\
directory \\
successExitValue \\
successExitValues \\
theExitValue \\
%\midrule
% operators
}

Executes the specified external \Arg{command} in a separate process with the
specified environment and working directory. The \Arg{command} contains the
name of the command to be looked up by the system or the full path of the command.
Any arguments for the command should be specified in \Arg{command}.

The \Arg{handler} is called when the process completes or when the process 
fails. The success return value
or a list of possible success return values of the process can be set by 
the \Arg{successExitValue} or by the \Arg{successExitValues} argument.
An handler must be set if the command is executed in the background by the \Operator*{background()}
operator, otherwise it is possible that the script will finish before the command itself finishes,
resulting in killing the command forcefully.

The \Arg{destroyer} can terminate the process under certain conditions.
The default destroyer will terminate the process if the JVM terminates under
any circumdances, see \code{Runtime}\code{\#addShutdownHook(Thread)}\cite{addshutdownhook13}.

An timeout can be set by the \Arg{timeout} argument. For special conditions
that can trigger a timeout the \Arg{watchdog} can be set. The default settings
is no timeout, meaning the build-in will wait for the process to terminate.

The environment as the system-dependent mapping from variables
to values can be set with the \Arg{env} argument. The initial value is a copy 
of the environment of the current script \Variable*{ENV}. Can be set to a map 
containing \code{key=value} entries.
The working directory of the process can be set by \Arg{path}. The default value
is the current working directory set by the \Command*{cd} command
and saved in the \Variable*{PWD} variable.

For interactive commands a terminal can be set. The \Arg{terminal} specifies
if an interactive terminal should be used for the command. The default terminal
will be used if no \Arg{terminalCommand} command is specified. Without the full
path the command is looked up in the current search path of the
script. Arguments for the command have to be specified. The command that should
be executed by the terminal will replace the \code{``\{\}''} characters in
the command string. The terminal to use can also be set with the environment
variable \Variable{TERMINAL\_COMMAND}.

\begin{asparaitem}
%
\item[\code{handler: handler}] \hfill \\
the \Type{ExecuteResultHandler}\cite{executeresulthandler13} or of a class 
type; the class type is instantiated with the default
constructor and set as the handler. Defaults to the 
\Type{DefaultExecuteResultHandler}\cite{defaultexecuteresulthandler13}.
%
\item[\code{destroyer: destroyer}] \hfill \\
the \Type{ProcessDestroyer}\cite{processdestroyer13} or of a class 
type; the class type is instantiated with the default
constructor and set as the handler.
Defaults to the \Type{ShutdownHookProcessDestroyer}\cite{shutdownhookprocessdestroyer13}
%
\item[\code{watchdog: watchdog}] \hfill \\
the \Type{ExecuteWatchdog}\cite{executewatchdog13} or of a class 
type; the class type is instantiated with the default
constructor and set as the handler.
Defaults to no watchdog.
%
\item[\code{timeout: duration}] \hfill \\
the timeout in milliseconds or of \Type{Duration}\cite{duration13}.
Defaults to \code{ExecuteWatchdog}\code{\#INFINITE\_TIMEOUT}.
%
\item[\code{command}] \hfill \\
the command to execute, with additional arguments.
%
\item[\code{env}] \hfill \\
map containing \code{key=value} entries for the environment.
%
\item[\code{path}] \hfill \\
the path of the working directory for the process.
%
\end{asparaitem}

\begin{lstlisting}[style=Groovybash, label={lst:example_exec1}, title={
Examples to execute external commands.}]
exec "ls -al"
exec "javap -private", "/home/user/java6/bin"
exec "mvn package", [JAVA_HOME: "/home/user/java6"]
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_exec2}, title={
Deleyed execution of external commands.}]
def command = exec.args "ls -al"
command.directory = "/tmp"
command.timeout = 500
command()
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_exec3}, title={
Execute command with an interactive terminal.}]
export TERMINAL_COMMAND, "konsole --nofork --hide-menubar --hide-tabbar -e {}"
exec terminal: true, "fsck /dev/sda1"
exec terminal: true, terminalCommand: "mrxvt -e {}", "fsck /dev/sda1"
\end{lstlisting}

