\TheCommand{device}%
\Command{device [type: string] [, loop: path] , path [, args...]}

\TypeTable{device \\}{%
% properties
type \\
device \\
loop \\
theType \\
theDevice \\
theName \\
%\midrule
% operators
}

Creates a device for the specified device \Arg{path}. The \Arg{type}
of the device needs to be set; as an alternative the device \Arg{path}
can be an URI which scheme part is used as the device type.
The \Arg{args...} arguments are passed on to the device.

If the device path is a regular file and the device type is not a loop device, 
then the file is assumed to be an image file for which a loop device is 
first created using the \Command*{loop} command. The loop device will be the
next available loop device, if nothing was specified in the \Arg{loop} argument.
After the loop device was created, the specified device type is created.
The \code{file}\cite{mancxfile13} tool is used to identify the file type.

All additional arguments are passed on directly to the device, like passwords,
loop device name, etc. Furthermore, after the device is created, operations
and properties not defined in the command are passed on to the underlying device.

The command will return the device for additional operators on the device
with the property \Operator{theDevice}. The type of the returned device is 
dependend on the type specified:

\begin{asparaitem}
%
\item \qcode{block} see \Command*{block} device;
\item \qcode{crypt} see \Command*{crypt} device;
%\item[\qcode{mdrain}] see \Command*{block} command;
%
\end{asparaitem}


\begin{asparadesc}
%
\item[\code{type}] \hfill \\
the device type.
%
\item[\code{loop}] \hfill \\
the loop path.
%
\item[\code{device}] \hfill \\
the device path.
%
\item[\code{theType}] \hfill \\
returns the device type.
%
\item[\code{theDevice}] \hfill \\
returns the device.
%
\item[\code{theName}] \hfill \\
returns the name of the command.
%
\item[\code{FILE\_COMMAND}] \hfill \\
the path of the \code{file} tool.
%
\end{asparadesc}

\input{device_block_en}
\input{device_crypt_en}

\begin{lstlisting}[style=Groovybash, label={lst:example_device1}, title={
Creates a block device for the device path.}]
def device = device type: "block", "/dev/sda1"// or
def device = device "block:///dev/sda1"
def block = device.theDevice
block.autoFsck()
block.mount "/media/sda1"
// alternative
def device = device "block:///dev/sda1"
device.autoFsck()
device.mount "/media/sda1"
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_device2}, title={
Creates a block device for the device path and apply operations on it, short syntax}]
device "block:///dev/sda1" autoFsck()
device "block:///dev/sda1" mount "/media/sda1"
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_device2}, title={
Creates a loop device for the image file.}]
def block = device "block://image.dd" theDevice
def block = device loop: "loop1", "block://image.dd" theDevice
def block = device type: "block", loop: "loop1", "image.dd" theDevice
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_device3}, title={
Passing of arguments to the created device.}]
def crypt = device type: "crypt", "file://image.dd", "password" theDevice
crypt.mount "/media/image"
\end{lstlisting}
