\TheCommand{enable}%
\Command{enable [disable: true|false] [delete: true|false] [library:\\ filename] [classpath: path] [names...]}

\TypeTable{enable \\}{%
% properties
theCommands \\
%\midrule
% operators
}

Enables or disables specific build-in commands. Disabled build-in commands
are allowing an external command to be executed in place of the build-in.
If \Arg{disable} is set to \TypeTrue the specified \Arg{names} will be disabled;
otherwise the \Arg{names} are enabled. 

If either \Arg{library} or \Arg{classpath}
are specified then the \Arg{names} are loaded and enabled from the libraries.
The \Arg{delete} argument will delete the previosly loaded build-in if set to \TypeTrue.

Without arguments the list of currently loaded and active build-in commands
is available. The list will contain the names of build-in commands and one of the 
\Type*{CommandStatus} status:

\begin{compactitem}
%
\item \Type{CommandStatus.enabled}
if the build-in command is enabled;
%
\item \Type{CommandStatus.disabled}
if the build-in command is disabled;
%
\item \Type{CommandStatus.loaded}
if the build-in command is loaded from a library and enabled;
%
\end{compactitem}


\begin{asparadesc}
%
\item[\code{disable: true|false}] \hfill \\
disable the \Arg{names} build-in commands if set to \TypeTrue; otherwise
enable the \Arg{names} build-in commands. Defaults to \TypeFalse.
%
\item[\code{delete: true|false}] \hfill \\
deletes the previosly loaded build-in commands with the 
specified \Arg{names}. Defaults to \TypeFalse.
%
\item[\code{library: filename}] \hfill \\
loads and enables the \Arg{names} build-in commands from the specified 
library file. If no \Arg{names} are specified, then all found build-in 
commands are loaded.
%
\item[\code{classpath: path}] \hfill \\
loads and enables the \Arg{names} build-in commands from the specified 
class path. If no \Arg{names} are specified, then all found build-in 
commands are loaded.
%
\item[\code{names...}] \hfill \\
the names of the build-in commands that should be enabled, disabled,
loaded or deleted.
%
\item[\code{theCommands}] \hfill \\
a list of all enabled, disabled or loaded build-in commands.
%
\end{asparadesc}

\begin{lstlisting}[style=Groovybash, label={lst:example_enable1}, title={%
Disables and enables build-in commands.}]
enable disable: true, "cd"
enable "cd"
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_enable2}, title={%
Loads build-in commands from libraries.}]
enable library: "SomeCommand.jar"
enable classpath: "my/path", "some"
\end{lstlisting}

\begin{lstlisting}[style=Groovybash, label={lst:example_enable3}, title={%
Print all enabled build-in commands.}]
enable.theCommands.findAll { 
    it.value == CommandStatus.ENABLED 
}.each {
    echo it
}
\end{lstlisting}

