\section{Commands}

Commands are identifier that are not class, interface, methods names or Java
or Groovy key-words or build-in variables. There are two kinds of commands:
external commands and build-in commands.

External commands are executes as a separated process, either in the foreground
or in the background. External commands are only available if found in the
search path or in the current working directory.
Build-in commands are always available and are executed in the current process.
Build-ins are like functions or methods that can be executed.

\subsection{Flags}

\paragraph{\code{in: Object|File|Stream}}

Redirects the standard output to a
file or a stream. If a generic \code{Object} is specified, the string
representation of this object is used as file name for the redirect target.

\subparagraph{Example:}

\begin{lstlisting}[style=Groovybash, label={lst:example_flag_in}]
echo out: "output.txt", "Hello World"

output = new ByteArrayOutput Stream()
echo out: output, "Hello World"
\end{lstlisting}

\paragraph{\code{out: Object|File|Stream}}

Redirects the standard output to a
file or a stream. If a generic \code{Object} is specified, the string
representation of this object is used as file name for the redirect target.

\subparagraph{Example:}

\begin{lstlisting}[style=Groovybash, label={lst:example_flag_out}]
echo out: "output.txt", "Hello World"

output = new ByteArrayOutput Stream()
echo out: output, "Hello World"
\end{lstlisting}

\paragraph{\code{err: Object|File|Stream}}

Redirects the standard output to a
file or a stream. If a generic \code{Object} is specified, the string
representation of this object is used as file name for the redirect target.

\subparagraph{Example:}

\begin{lstlisting}[style=Groovybash, label={lst:example_flag_err}]
echo err: "error.txt", "Hello World"

output = new ByteArrayOutput Stream()
echo err: output, "Hello World"
\end{lstlisting}

\paragraph{\code{fromIn: true|false}}

Reads the first line from the standard input and injects it as the first
arguments for the command.

\subparagraph{Example:}

\begin{lstlisting}[style=Groovybash, label={lst:example_flag_fromin}]
echo fromIn: true
run fromIn: true
\end{lstlisting}

\subsection{Return Value}

External and build-in commands returning a return value from type
\code{ReturnValue}. The most basic return value contains only a human readable
representation of the status of the command.

Most commands return \code{ReturnCode} as the return value. It contains a number
value as the return code from the command. As a convention the
code \code{0} is equavalent to the value \code{true} and any value not \code{0}
is equavalent to \code{false} and is representing an error code.
