\subsection{Stream Redirection}

All commands have three standard streams: standard input, standard output
and error output streams. Those streams can be redirected to a different stream
or file. The operators \code{<, >, <<, >>, |} are redirecting streams to a
different stream or file.

\Operator{left < right}
The \TheOperator{<} redirects the standard input stream of
the left to the object specified on the right side. If on the left side is
a command, then the right side can be of type \TypeStream, \TypeFile, \TypeReturnValue
or of \TypeGenericObject. The \TypeStream will be read until the end of the stream
is reached; the \TypeFile will be open and the content of the file is read;
the \TypeReturnValue will read the standard output stream of the return value;
if the left side is neither of the three types then the \TypeGenericObject is
converted to a string and the string is written to the standard input of the
command.

If the command is on the right side then the standard output of the command
can redirected to a \TypeStream, \TypeFile or another command. For \TypeStream
the output of the command is written to the stream; for \TypeFile the file
is opened and the output is written to the file.
For commands on both sides, the output of the right command is written to 
the standard input of the left command.

\begin{lstlisting}[style=Groovybash, label={lst:example_input_op}, caption={Example \OperatorName <}]
echo < stream
echo < file
echo < "Some Text"
stream < echo "Some Text"
file < echo "Some Text"
echo < echo "Some Text"
\end{lstlisting}

\Operator{left > right}
The \TheOperator{>} redirects the standard output stream of
the left to the object specified on the right side. If on the left side is
a command, then the right side can be of type \TypeStream, \TypeFile
or of \TypeGenericObject. For \TypeStream the output will be written in the stream; 
for \TypeFile the file will be open and the output will be written to the file;
if the right side is neither of the two types then the \TypeGenericObject is
converted to a string and the string is used as a file name. The file will be
open and the output will be written to the file.

If the command is on the right side then the standard input of the command
is filled with the data from a \TypeStream, \TypeFile or another command. 
For \TypeStream the stream is red to the standard input of the command until the stream
reached its end; for \TypeFile the file is opened and the content of the file is
written to the standard input of the command; if on both sides is a command
then the standard output of the left command is redirected to the standard
input of the right command.

If on the left side is neither a \TypeStream, \TypeFile or another command
the \TypeGenericObject is converted to a string and the string is used as a
file name. The file opened and the content of the file is written to the
standard input of the command.

\begin{lstlisting}[style=Groovybash, label={lst:example_output_op}, caption={Example \OperatorName >}]
echo > stream
echo > file
echo > "file_name"
stream > cat
file > cat
"Some Text" > echo
echo "Some Text" > echo
\end{lstlisting}

\Operator{left << right}
The \TheOperator{<<} redirects the standard output stream of the left to 
the object specified on the right side, like the \TheOperator*{<}, but
files and streams are appended instead of overridden.

\Operator{left >> right}
The \TheOperator{>>} redirects the standard output stream of
the left to the object specified on the right side, like the \TheOperator*{>}, but
files and streams are appended instead of overridden.

\Operator{left | right}
The \TheOperator{|} creates a pipe between the left object and the right object.
It is possible to chain multiple object together. The result value will be the
result of the last object.

\begin{lstlisting}[style=Groovybash, label={lst:example_pipe_op}, caption={Example \OperatorName |}]
file > cat | echo
\end{lstlisting}



